---
title: "Project 3: myfirstpackage Tutorial"
author: "Cameron Sims"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{myfirstpackage Tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Introduction

This package was designed for my UW STAT 302 course's Project 3. It contains
four methods for performing statistical inference/prediction:
\begin{itemize}
\item Linear Regression
\item T-Test
\item K-Nearest Neighbors with Cross-Validation
\item Random Forests with Cross Validation
\end{itemize}

```{r, include = FALSE, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

To install this package through Github, use

```{r, eval = FALSE}
devtools::install_github("CamSims/myfirstpackage")
```

To begin, we load the package.

```{r setup}
library(myfirstpackage)
```

# my_t.test Tutorial

This section will demonstrate how to use the my_t.test() function.

```{r}
# Use the lifeExp data from my_gapminder
dat <- my_gapminder$lifeExp

# Demonstrate a test of the hypothesis H0: mu = 60, Ha: mu != 60
my_t.test(x = dat, alternative = "two.sided", mu = 60)
```
At a cutoff of $\alpha = 0.05$, the p-value of $0.0932$ means the null
hypothesis can not be rejected. In other words, $60$ is a valid value for $\mu$.

```{r}
# Demonstrate a test of the hypothesis H0: mu = 60, Ha: mu < 60
my_t.test(x = dat, alternative = "less", mu = 60)
```

Using the $\alpha = 0.05$ cutoff, the p-value of $0.0466$ means the null
hypothesis can be rejected. In other words, the data suggests $\mu$ is less than
$60$.

```{r}
# Demonstrate a test of the hypothesis H0: mu = 60, Ha: mu > 60
my_t.test(x = dat, alternative = "greater", mu = 60)
```

Using the $\alpha = 0.05$ cutoff, the p-value of $.9533$ means the null
hypothesis can not be rejected. The data suggests $mu = 60$ is a valid value.
